### 2015-07-26 ms-thesis/ver2/intro/ms-thesis-intro.tex
-

ISE and DJI data sets consisted of daily closing prices for over 21 years for
ISE and 30 years for DJI. DJI data was obtained from
\PVerb!http://finance.yahoo.com! site. ISE-100 historical data is available from
Turkish Central Bank site at \PVerb!http://evds.tcmb.gov.tr!. We attempted to
predict future price for 1, 5, and 10 days for each method mentioned above. All
methods were given a limited ``time window'' on which training took place, after
which, prediction for future prices could be performed. We kept the training
window the same size for all algorithms with the exception of ANN because too
much data was causing overfitting and effecting results negatively.

@@

@@

In order to fit the model to the data, the modeler first decides the order of
the polynomial equation (we used 10). Then, a least squares fit is performed
which aims to minimize the error $\epsilon$. At the end this process outputs all
$\beta$ coeffecients to define the equation for $y$. Matlab's \PVerb!polyfit!
accomplished this task.

>>>>

ISE and DJI data sets consisted of daily closing prices for over 21 years
for ISE and 30 years for DJI. DJI data was obtained from
\url{http://finance.yahoo.com} site. ISE-100 historical data is available
from Turkish Central Bank site at \url{http://evds.tcmb.gov.tr}. We
attempted to predict future price for 1, 5, and 10 days for each method
mentioned above. All methods were given a limited ``time window'' on which
training took place, after which, prediction for future prices could be
performed. We kept the training window the same size for all algorithms
with the exception of ANN because too much data was causing overfitting and
effecting results negatively.

@@

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../data/ise.csv',index_col='Date')
df['Adj Close'].head(1000).plot()
plt.hold(False)
plt.savefig('ms-thesis-intro_01.png')
plt.hold(False)
\end{minted}

\includegraphics[height=6cm]{ms-thesis-intro_01.png}

@@

In order to fit the model to the data, the modeler first decides the order of
the polynomial equation (we used 10). Then, a least squares fit is performed
which aims to minimize the error $\epsilon$. At the end this process outputs all
$\beta$ coeffecients to define the equation for $y$. Matlab's \verb!polyfit!
accomplished this task.
